---
title: "p8105_hw5_sw3455"
author: "Shiying Wu"
date: "2024-11-13"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(httr)
library(ggplot2)
library(tidyverse)
library(broom)
set.seed(1)
```

```{r problem1}
birthday = function(n) {
  bdays = sample(1:365, size = n, replace = TRUE)
  duplicate = length(unique(bdays)) < n           
  return(duplicate)
}

output <- vector("list", 49)

for (i in 2:50) {
  results <- 0 
  for (j in 1:10000){
  if (birthday(i)) {results = results + 1}
  }
  output[[i - 1]] <- tibble(size = i, prob = results / 10000)
}

bind_rows(output)|>
  ggplot(aes(x = size, y = prob)) +
  geom_line() +
  labs(title = "Probability of Sharing a Birthday",
       x = "Group Size",
       y = "Probability") +
  theme_minimal()
```
As number of people increase, the probability also increases exponentially. Surprisingly when there’s 50 people in the room, the probability is almost 1.


```{r problem2 function}
ttest = function(mu) {
  ttest_output <- vector("list", 5000)
  for (i in 1:5000) {
  data <- rnorm(30, mean = mu, sd = 5)
  table <- t.test(data, mu = 0)|>
    broom::tidy() |>
    select(estimate, p.value)
  ttest_output[[i]] <- tibble(mu = mu, table)
  }
  return(bind_rows(ttest_output))
}

ttest_output <- vector("list", 7)
for (i in 0:6) {
    ttest_output[[i+1]] <- ttest(i)}
ttest_result <- bind_rows(ttest_output)
```

```{r problem2 plot1, fig.width = 8, fig.asp = 0.6}
ttest_result |>
  group_by(mu) |>
  summarise(power = mean(p.value < 0.05)) |>
  ggplot(aes(x = mu, y = power)) +
  geom_point() +
  geom_line() +
  labs(x = "Mu",
       y = "Power") +
  theme_minimal()
```
As the effect size increases (meaning the true mean mu  be larger away from the null hypothesis mean  0), the power of the test increases(higher proportion  of rejection) exponentialy. As true mean reach more than 4, the rejection more and more close to 1.


```{r problem2 plot2, fig.width = 8, fig.asp = 0.6}
ttest_result |>
  group_by(mu) |>
  summarise(Sample_Mean = mean(estimate)) |>
  ggplot(aes(x = mu, y = Sample_Mean)) +
  geom_point() +
  geom_line() +
  labs(x = "Mu",
       y = "Sample Mean") +
  theme_minimal()

ttest_result |>
  filter(p.value < 0.05) |>
  group_by(mu) |>
  summarise(Sample_Mean = mean(estimate)) |>
  ggplot(aes(x = mu, y = Sample_Mean)) +
  geom_point() +
  geom_line() +
  labs(x = "Mu",
       y = "Sample Mean") +
  theme_minimal()

```
On the plot 2, mean of each 5000 sample mean is really close to their true mean. Compare to plot 3 for the rejected sample it is significantly more or less then their true mean as line is not a straight line before 4, however, after 4, the sample mean are similar to their ture mean and similar line as plot 2.

```{r problem 3 rawdata}
homicides = read.csv("./data/homicide-data.csv",
        na = c(".", "NA", "")) |>
  janitor::clean_names() 

```
The data has have `r ncol(homicides)` columns which means have `r ncol(homicides)` variables and `r nrow(homicides)` rows means `r nrow(homicides)` criminal homicides. The `r ncol(homicides)` variables are `r colnames(homicides)`. It including date and location for the homicides, geograophic imformation about victim and situation of homicides whether it is closed or still open. 

```{r problem 3 new variable}
homicide_df <- homicides |>
  mutate(city_state = paste(city, state, sep = ", ")) |>
  filter(city_state != "Tulsa, AL") |>
  group_by(city_state) |>
  summarise(
    total_homicides = n(),
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  )
```
There is only one cases in Tulsa, AL, and after googling, there is no Tulsa city in AL which count as a mistake

```{r problem 3 Baltimore}
proptest = function(unsolved_homicides, total_homicides) {
  prop_test = prop.test(unsolved_homicides, total_homicides) |>
  broom::tidy(prop_test) |>
  select(estimate, conf.low, conf.high)
  return(tibble(prop_test))
}

Baltimore_df <- homicide_df |>
  filter(city_state == "Baltimore, MD")

Baltimore_result <-
  proptest(Baltimore_df$unsolved_homicides, Baltimore_df$total_homicides)
```

```{r problem 3 overall}
overall_results =
  homicide_df |>
  mutate(results = purrr::map2(unsolved_homicides, total_homicides, proptest)) |>
  unnest(results)|>
  select(city_state, estimate, conf.low, conf.high)
```

```{r problem 3 PLotting, fig.width = 8, fig.asp = 1}
overall_results|>
  arrange(desc(estimate))|>
  ggplot(aes(x = fct_reorder(city_state, estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.5) +
  coord_flip() + 
  labs(x = "City",
       y = "Proportion of Unsolved Homicides") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 11))
```
